Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-06-24 Submission.Rmd
not perfect but all correlations shown (deleted p<.001 with ***)

r <- corx::corx(data_new, x =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo",  "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"), y =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo", "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"),            
                triangle = "lower",
 #               stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
                  caption = "Challenge, hindrance, and resource bivariate correlations.",
                  escape = FALSE, 
                  font_size = "tiny",  ## "tiny" smallest
                  longtable = TRUE,
                  landscape = TRUE,
#                  stub_indents = list(a=1:10, b = 11:21),
                  note = "The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
trial <- data_new[c(405:411, 413:419, 421:427)]
#library(apaTables)
#apa.cor.table(trial, filename = "cor.doc", show.conf.interval = FALSE, landscape = TRUE)

>>>>

r <- corx::corx(data_new, x =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo",  "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"), y =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo", "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"),            
                triangle = "lower",
                stars = c(0.05, 0.01)) #, 0.001),
 #               describe = c(`$M$` = mean, `$SD$` = sd))

#rapa <- as.data.frame(r$apa)

papaja::apa_table(r$apa, # changed from r$apa list 6/23/24
                  caption = "Challenge, hindrance, and resource bivariate correlations.",
                  escape = FALSE, 
                  font_size = "tiny",  ## "tiny" smallest
                  longtable = TRUE,
                  landscape = TRUE,
#                  stub_indents = list(a=1:10, b = 11:21),
                  align = c("m{2.6cm}", rep("m{.7cm}",21)),
                  note = "$*$ p < .05, $**$ p < .01; The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
trial <- data_new[c(405:411, 413:419, 421:427)]
#library(apaTables)
#apa.cor.table(trial, filename = "cor.doc", show.conf.interval = FALSE, landscape = TRUE)

### 2024-06-24 Submission.tex
not perfect but all correlations shown (deleted p<.001 with ***)

\begin{TableNotes}[para]
\normalsize{\textit{Note.} The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)}
\end{TableNotes}

@@

\begin{longtable}{lllllllllllllllllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}

@@

 & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\

@@

1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
2. onet.resource.mp & .61*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
3. onet.resource.wo & .46*** & .50*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
4. onet.resource.io & .49*** & .64*** & .45*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
5. onet.resource.ir & .46*** & .55*** & .37*** & .60*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
6. onet.resource.pc & .19*** & .15*** & .32*** & .18*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
7. onet.resource.sc & .43*** & .46*** & .41*** & .45*** & .48*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
8. onet.challenge.ii & .62*** & .49*** & .37*** & .41*** & .33*** & .08 & .33*** & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
9. onet.challenge.mp & .47*** & .63*** & .42*** & .50*** & .41*** & .09* & .38*** & .65*** & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
10. onet.challenge.wo & .34*** & .39*** & .64*** & .34*** & .30*** & .29*** & .38*** & .45*** & .49*** & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
11. onet.challenge.io & .34*** & .48*** & .33*** & .65*** & .48*** & .13** & .40*** & .50*** & .68*** & .43*** & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
12. onet.challenge.ir & .32*** & .40*** & .26*** & .48*** & .63*** & .23*** & .39*** & .46*** & .60*** & .39*** & .70*** & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
13. onet.challenge.pc & .12** & .08 & .21*** & .13** & .26*** & .66*** & .29*** & .14** & .12** & .33*** & .20*** & .31*** & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
14. onet.challenge.sc & .27*** & .31*** & .28*** & .38*** & .40*** & .27*** & .62*** & .36*** & .41*** & .38*** & .51*** & .45*** & .40*** & - &  &  &  &  &  &  & 3.66 & 0.59\\
15. onet.hindrance.ii & -.26*** & -.26*** & -.17*** & -.24*** & -.18*** & -.02 & -.08 & -.27*** & -.26*** & -.10* & -.19*** & -.16*** & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
16. onet.hindrance.mp & -.23*** & -.30*** & -.17*** & -.22*** & -.15*** & .05 & -.07 & -.22*** & -.27*** & -.10* & -.18*** & -.15*** & .12** & -.06 & .86*** & - &  &  &  &  & 2.10 & 1.05\\
17. onet.hindrance.wo & -.21*** & -.25*** & -.22*** & -.22*** & -.06 & -.02 & -.12** & -.14** & -.21*** & -.23*** & -.15*** & -.09* & .05 & -.10* & .66*** & .69*** & - &  &  &  & 2.31 & 1.02\\
18. onet.hindrance.io & -.22*** & -.27*** & -.14*** & -.29*** & -.18*** & -.01 & -.10* & -.21*** & -.25*** & -.10* & -.27*** & -.19*** & .07 & -.10* & .79*** & .86*** & .69*** & - &  &  & 2.23 & 1.03\\
19. onet.hindrance.ir & -.22*** & -.24*** & -.15*** & -.24*** & -.25*** & -.06 & -.11** & -.19*** & -.21*** & -.08* & -.20*** & -.23*** & .04 & -.12** & .79*** & .80*** & .61*** & .82*** & - &  & 2.35 & 0.89\\
20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16*** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38*** & .33*** & .47*** & .35*** & .47*** & - & 2.66 & 0.83\\
21. onet.hindrance.sc & -.13** & -.15*** & -.13** & -.19*** & -.13** & -.09* & -.23*** & -.12** & -.10* & -.05 & -.16*** & -.12** & -.01 & -.17*** & .62*** & .62*** & .56*** & .64*** & .66*** & .45*** & 2.64 & 0.80\\

>>>>

\begin{TableNotes}[para]
\normalsize{\textit{Note.} $*$ p < .05, $**$ p < .01; The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)}
\end{TableNotes}

@@

\begin{longtable}{m{2.6cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}

@@

 & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20}\\

@@

1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
2. onet.resource.mp & .61** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
3. onet.resource.wo & .46** & .50** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
4. onet.resource.io & .49** & .64** & .45** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
5. onet.resource.ir & .46** & .55** & .37** & .60** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
6. onet.resource.pc & .19** & .15** & .32** & .18** & .37** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
7. onet.resource.sc & .43** & .46** & .41** & .45** & .48** & .37** & - &  &  &  &  &  &  &  &  &  &  &  &  & \\
8. onet.challenge.ii & .62** & .49** & .37** & .41** & .33** & .08 & .33** & - &  &  &  &  &  &  &  &  &  &  &  & \\
9. onet.challenge.mp & .47** & .63** & .42** & .50** & .41** & .09* & .38** & .65** & - &  &  &  &  &  &  &  &  &  &  & \\
10. onet.challenge.wo & .34** & .39** & .64** & .34** & .30** & .29** & .38** & .45** & .49** & - &  &  &  &  &  &  &  &  &  & \\
11. onet.challenge.io & .34** & .48** & .33** & .65** & .48** & .13** & .40** & .50** & .68** & .43** & - &  &  &  &  &  &  &  &  & \\
12. onet.challenge.ir & .32** & .40** & .26** & .48** & .63** & .23** & .39** & .46** & .60** & .39** & .70** & - &  &  &  &  &  &  &  & \\
13. onet.challenge.pc & .12** & .08 & .21** & .13** & .26** & .66** & .29** & .14** & .12** & .33** & .20** & .31** & - &  &  &  &  &  &  & \\
14. onet.challenge.sc & .27** & .31** & .28** & .38** & .40** & .27** & .62** & .36** & .41** & .38** & .51** & .45** & .40** & - &  &  &  &  &  & \\
15. onet.hindrance.ii & -.26** & -.26** & -.17** & -.24** & -.18** & -.02 & -.08 & -.27** & -.26** & -.10* & -.19** & -.16** & .06 & -.10* & - &  &  &  &  & \\
16. onet.hindrance.mp & -.23** & -.30** & -.17** & -.22** & -.15** & .05 & -.07 & -.22** & -.27** & -.10* & -.18** & -.15** & .12** & -.06 & .86** & - &  &  &  & \\
17. onet.hindrance.wo & -.21** & -.25** & -.22** & -.22** & -.06 & -.02 & -.12** & -.14** & -.21** & -.23** & -.15** & -.09* & .05 & -.10* & .66** & .69** & - &  &  & \\
18. onet.hindrance.io & -.22** & -.27** & -.14** & -.29** & -.18** & -.01 & -.10* & -.21** & -.25** & -.10* & -.27** & -.19** & .07 & -.10* & .79** & .86** & .69** & - &  & \\
19. onet.hindrance.ir & -.22** & -.24** & -.15** & -.24** & -.25** & -.06 & -.11** & -.19** & -.21** & -.08* & -.20** & -.23** & .04 & -.12** & .79** & .80** & .61** & .82** & - & \\
20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38** & .33** & .47** & .35** & .47** & -\\
21. onet.hindrance.sc & -.13** & -.15** & -.13** & -.19** & -.13** & -.09* & -.23** & -.12** & -.10* & -.05 & -.16** & -.12** & -.01 & -.17** & .62** & .62** & .56** & .64** & .66** & .45**\\
